Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Ajout city detection et angle crit

\newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
\newacronym{anfr}{ANFR}{French National Frequency Agency}
\newacronym{bs}{BS}{\Gls{base station}}

@@

You can find an illustration of this method in figure \ref{del_tri}.
\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_graphs/Delaunay_circumcircles_vectorial.svg.png}
    \caption{Example of a Delaunay triangulation}
    \label{del_tri}
\end{figure}

@@

\subsubsection{DBScan}

\subsubsection{HDBScan}

\subsubsection{$3$-NN mean distance}
One provider $\gamma$

To classify each base station we need a method. Here, we will take the mean distance to the 3 nearest neighbours.

Let's call this value $\gamma$, in $\unit{km}$. So, we have 4 different categories.
For each category, we will apply a different distance and angle criterion :

@@

\subsubsection{Angle criterion}
For each \acrshort{bs}, we

>>>>

\newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
\newacronym{anfr}{ANFR}{French National Frequency Agency}
\newacronym{bs}{BS}{\Gls{base station}}
\newacronym{dbscan}{DBScan}{Density-Based Spatial Clustering of Applications with Noise}
\newacronym{hdbscan}{HDBScan}{Hierarchical Density-Based Spatial Clustering of Applications with Noise}

@@

You can find an illustration of this method in Figure~\ref{del_tri}.
\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_graphs/Delaunay_circumcircles_vectorial.svg.png}
    \caption{Example of a Delaunay triangulation}
    \label{del_tri}
\end{figure}

@@

\subsubsection{\acrshort{dbscan}}
When thinking of density-based clustering, one of the first methods that comes in mind is probably \acrshort{dbscan}.
It is really powerful because we only have two parameters to modify.

Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered in a city or not.
We wanted a more continuous method.

\subsubsection{\acrshort{hdbscan}}

\subsubsection{$3$-NN mean distance}
To classify each base station we need a method.

For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.

To make this method working properly, only \acrshort{bs} from one provider have to be kept into the calculation process.
Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, values could be modified.

@@

\subsubsection{Angle criterion}
For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{crit_ang}.
